---
output: github_document
editor_options: 
  chunk_output_type: console
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(epoxy)
```

# fsmglobal

<!-- badges: start -->

<!-- badges: end -->

## Overview

This data was first published as part of a journal article by [@greene2021] and contained in the supplemental material as a table in a DOCX file.

## Installation

You can install the development version of fsmglobal from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/fsmglobal")
```

Alternatively, you can download the individual datasets as a CSV or XLSX file from the table below.

```{r, echo=FALSE}

extdata_path <- "https://github.com/Global-Health-Engineering/fsmglobal/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  mutate(file_name = str_remove(file_name, ".rda")) |> 
  rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()
```

## Data

The package provides access to one dataset.

```{r}
library(fsmglobal)
```

```{epoxy}
The `fsmglobal` data set has {ncol(fsmglobal)} variables and {nrow(fsmglobal)} observations. For an overview of the variable names, see the following table.  
```

```{r, eval=FALSE}
fsmglobal
```

```{r, echo=FALSE}
readr::read_csv("data-raw/dictionary.csv") |> 
  dplyr::filter(file_name == "fsmglobal.rda") |> 
  dplyr::select(variable_name:description) |> 
  knitr::kable()
```

## License

Data are available as
[CC-BY](https://github.com/Global-Health-Engineering/fsmglobal/blob/main/LICENSE.md).

## References
